\documentclass{article}

\title{Part 3 Written Section}
\author{Corbin T. Rochelle (ctr233)}
\date{\today}

\begin{document}
\maketitle

\section*{Question 1}
The first part, and longest, was developing the classes and modifying the old code from part 2 to accept and return the classes.
This was the hardest part because I did not organize my files well, which led to a lot of problems with head file inclusion and the "os" operator not wanting to work. 
For this and all other sections I did a top-down development.
Next, I modified the original file to store the information into the classes. 
This was the fastest and easiest section.
Then I called the information.
I did not understand what classes needed to use the os operator or printTo, so I spent a while trying to figure that out.
Once I finally understood it, I correctly implanted it to where the correct information was displayed to the screen.
The last and most tedious section was correctly formatting the correct information once printed to match all of the reference files. 
The only functions that I wrote was a new ident function, printTo functions, and the overloaded os functions. 

\section*{Question 2}
The most difficult classes to write were the classes involving a switch statement (statement, simple expression, etc.).
This is because I created the class inside the statement, which threw errors for a long time because they were not correctly initialized. 
However, once I realized that I could bracket them off, it allowed to run since the other switch statements could no longer see the declarations before they were needed. 
The easiest nodes to write were statement and block since they only required to store one pointer to another class.  

\section*{Question 3}
The main insight that I gained from storing this information was that this is a lot harder than I imagined. 
I originally went into the assignment thinking it would take me 2-3 hours to complete.
It ended up taking me 7.
This is not because the logic behind this process was hard, but because I did not understand the syntax of c++ well enough.
Every problem I ran into was a syntax issue.

\section*{Question 4}
I did not use any sources that were not given by the professor or from previous project sections. 


\end{document}